Spatial Reasoning and Statistical Graphics

### 2014-10-08 Paper/Draft1/TestingVisualAptitude.Rnw
Additional information about test scoring

\section{Results}
We have tested 18 students, and plan to increase sample size once the summer semester begins. Preliminary results are presented graphically in figures \ref{fig:visualaptitudects} and \ref{fig:visualaptitudecat}. Scoring for all of the tests was calculated such that with random guessing, the expected score on a problem would be 0; thus, for a test with possible answers A, B, C, D, and E, the score would be calculated by subtracting $1/4*\text{\# wrong answers}$ from the total number of correct answers. This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses.

>>>>

\section{Results}
We have tested 18 students, and plan to increase sample size once the summer semester begins. Preliminary results are presented graphically in figures \ref{fig:visualaptitudects} and \ref{fig:visualaptitudecat}. Scoring for all of the tests was calculated such that with random guessing, the expected score on a problem would be 0; thus, for a test with possible answers A, B, C, D, and E, the score would be calculated by subtracting $1/4*\text{\# wrong answers}$ from the total number of correct answers. This allows us to compare each participant's score in light of how many problems were attempted as well as the number of correct responses. The scoring mechanism is also used on many standardized tests (the SAT, ACT, and the battery of psychological tests which certain sections of this test are drawn from); the ability to combine both accuracy and number of questions attempted into a single number makes comparing test scores much easier. In general, the formula for computing the score would be $$1/(n-1)*(\text{\# wrong answers}) + (\text{\# correct answers})$$ where $n$ is the total number of possible answers.
